The core transcriptome of the mammal placenta

### 2016-08-12 manuscript/manuscript.Rnw
add possible linebreak after ENS
add rodent table

                                         xtable.sanitize.text(name_or_id),"}}")]

@@

mentioned.genes.table[,species:=paste0("\\textit{",gsub("^(.)","\\U\\1",species,perl=TRUE),"}")]

@@

output.mentioned.genes.table <- function(subset.table=quote(TRUE),
                                         human.symbol=TRUE) {
    mgt.subset <- mentioned.genes.table[eval(subset.table)]
    mgt.display <- c("s","s","s","s","d","d")
    mgt.align <- c("c","c",
                   ">{\\raggedright \\centering}p{0.5in}",
                   ">{\\raggedright \\centering}p{0.5in}",
                   ##">{\\raggedright}p{4in}",
                   "r","r")
    if (!human.symbol) {
        mgt.subset[,`Human Symbol`:=NULL]
        mgt.display <- mgt.display[-4]
        mgt.align <- mgt.align[-4]
    }

@@

\begin{table}
\footnotesize
<<primate.genes,echo=FALSE,results="asis">>=
output.mentioned.genes.table(subset.table=quote(grepl("Homo|Ateles|Pan",Species)),
                             human.symbol=FALSE
                             )
@ 
\caption{Notable genes ordered by species and \ac{FPKM}. Gene
  symbol is the gene symbol or Ensembl gene id. Human Name is the HUGO
  name corresponding to the human symbol. A complete table of 
  genes with \ac{FPKM} $\ge 50$ is located in the supplemental material }
\label{tab:notable_genes}
\end{table}

\begin{table}
  \footnotesize
<<primate.lineage.specific,echo=FALSE,results="asis">>=
pri.all.lin.spec <- placenta.lineage.specific.table("pri.all")
setkey(pri.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanation{primates}{all other analyzed species}}
\label{tab:primate_lineage_specific}
\end{table}

@@

\begin{figure}
<<psg.ctsl.evolution.tree,echo=FALSE,fig.width=16,fig.height=16,warning=FALSE,message=FALSE>>=
plot.label.size <- 3
axis.text.size <- 3.5

@@

>>>>

                                         gsub("(ENS[^0-9]+)","\\1\\\\linebreak[0]",
                                              xtable.sanitize.text(name_or_id)),"}}")]

@@

mentioned.genes.table[,species:=paste0("\\textit{",gsub("^(.)\\S+","\\U\\1.",species,perl=TRUE),"}")]

@@

output.mentioned.genes.table <- function(subset.table=quote(TRUE),
                                         human.symbol=TRUE) {
    mgt.subset <- mentioned.genes.table[eval(subset.table)]
    mgt.display <- c("s","s","s","s","d","d")
    mgt.align <- c("c","c",
                   ">{\\raggedright \\centering}p{0.5in}",
                   ">{\\raggedright \\centering}p{0.5in}",
                   ##">{\\raggedright}p{4in}",
                   "r","r")
    if (!human.symbol) {
        mgt.subset[,`Human Symbol`:=NULL]
        mgt.display <- mgt.display[-4]
        mgt.align <- mgt.align[-4]
        mgt.align[3] <- ">{\\raggedright \\centering}p{1.2in}"
    }

@@

\begin{table}[htb]
\footnotesize
<<primate.genes,echo=FALSE,results="asis">>=
output.mentioned.genes.table(subset.table=quote(grepl("sapiens|fusciceps|paniscus",Species)),
                             human.symbol=TRUE
                             )
@ 
\caption{Notable genes ordered by species and \ac{FPKM}. Gene
  symbol is the gene symbol or Ensembl gene id. Human Name is the HUGO
  name corresponding to the human symbol. A complete table of 
  genes with \ac{FPKM} $\ge 50$ is located in the supplemental material }
\label{tab:notable_primate_genes}
\end{table}

\begin{table}[htb]
  \footnotesize
<<primate.lineage.specific,echo=FALSE,results="asis">>=
pri.all.lin.spec <- placenta.lineage.specific.table("pri.all")
setkey(pri.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanation{primates}{all other analyzed species}}
\label{tab:primate_lineage_specific}
\end{table}

@@

\begin{figure*}
<<psg.ctsl.evolution.tree,echo=FALSE,fig.width=8,fig.height=8,warning=FALSE,message=FALSE>>=
plot.label.size <- 3
axis.text.size <- 3.5

@@

\begin{table}
  \footnotesize
<<rodentia.genes,echo=FALSE,results="asis">>=
output.mentioned.genes.table(subset.table=quote(grepl("musculus|galili|carmeli",Species)),
                             human.symbol=TRUE
                             )
@ 
\caption{Notable genes ordered by species and \ac{FPKM}. Gene
  symbol is the gene symbol or Ensembl gene id. Human Name is the HUGO
  name corresponding to the human symbol. A complete table of 
  genes with \ac{FPKM} $\ge 50$ is located in the supplemental material }
\label{tab:notable_non_primate_genes}
\end{table}
